Prefetching SPARQL query cacher

### 2016-05-25 dissertation/related.tex
dividino critisism

>>>>

Dividino et al. \cite{Dividino2015} proposed strategies to keep caches
of Linked Open Data up to date, in face of changing data. The authors
sets out to learn the change frequency of resources, and based on that
schedule updates of the resources. This does then not depend on the
resource metadata (neither HTTP headers nor metadata in the RDF
itself, which I studied in \cite{kjernsmo_survey_2015}), which is
motivated by their finding that only 8\% of \httph{Last-Modified}
headers they surveyed reflected the true change frequency. While I
have no reason to doubt this finding, and the monitoring approach is
interesting, I think the dismissal of resource metadata is
insufficiently motivated, and therefore the evaluation is
inadequate. First, the \httph{Last-Modified} header is far from the
only cache-relevant header, as should be evident by the fact that it
is not defined in the cache standard, RFC7234, but in the conditional
request standard, RFC7232. Moreover, RFC7234 contains a Section~4.2.2.
titled ``Calculating Heuristic Freshness''. It is my opinion that the
paper should be framed within the loose constraints of this section,
where it could make a substantial contribution. As it stands, it would
serve to violate Web standards, which in my opinion, is something the
Semantic Web community should be more cautious about. If further
considered within the frames of RFC7234's Section~4.2.2., it also
proposes a simple heuristic for calculating freshness lifetime. I
found that the distribution of this heuristic freshness lifetime
agrees well with The Dynamic Linked Data Observatory (DyLDO)
\cite{dyldo2}. However, a weakness of my study, which could make this
observation irrelevant, is if the change frequency of individual
resources were wrong, in particular, if the use of the simple
heuristic lead to using stale content.  RFC7234's
Section~4.2.2. explicitly prohibits the use of a heuristic if an
explicit expiration time is present (defined in the caching standard
RFC7234), yet the paper does not attempt to include those in their
assessment. Furthermore, I found in \cite{kjernsmo_survey_2015} that
cache prohibitions were common. While they in many cases may be
misguided, they nevertheless express a strong statement from the
server administrators, that should be respected. RDF data,
e.g. \rdfterm{dct:valid} and \rdfterm{dct:modified} could also be used
to compute a expiration time. Finally, an opaque validator,
\httph{ETag} is also a part of RFC7232. After considering cache
prohibitions, explicit expiration times, opaque validators, simpler
heuristics, etc., the space where learning the change frequency could
be applied is likely much smaller. However, if understood as a
sophisticated heuristic with the constraints of RFC7234's
Section~4.2.2., the contribution is valuable.
